ms-russia-figs-analysis

### 2024-04-19 ms-russia-figures.Rmd

ggsave(file.path(figdir, "fig1.png"), device = "png", width = 6.5, height = 5, unit = "in")
```

@@

```{r}
rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))

@@

ggsave(file.path(figdir, "fig2.png"), device = "png", width = 6.6, height = 6)
```

>>>>

ggsave(file.path(figdir, "fig1.png"), device = "png", width = 6.5, height = 5, unit = "in", dpi = 500)
```

@@

```{r}
rus_chn_usa <- read.csv(file.path(datadir, "rus_chn_usa.csv"))
chn_to_usa <- read.csv(file.path(datadir, "chn_to_usa.csv"))

@@

ggsave(file.path(figdir, "fig2.png"), device = "png", width = 6.6, height = 6, dpi = 500)
```
